Modelling Federal Open Market Committee Decisions Using ML and NLP

### 2019-05-04 presentation/presentation.tex
update

\usepackage{comment}
%usepackage{appendixnumberbeamer}
%\usepackage{amsmath}
\usepackage{pgfpages}
% citations
\usepackage{natbib}
\bibpunct{(}{)}{;}{a}{,}{,}
\def\citeapos#1{\citeauthor{#1}'s (\citeyear{#1})}
\renewcommand{\bibsection}{\subsubsection*{\bibname } }

@@

\begin{frame}

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{../output/data_for_graphs/Topic-Model-3-topics.PNG}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
\end{center}
\end{figure}

>>>>

\usepackage{comment}
%usepackage{appendixnumberbeamer}
%\usepackage{amsmath}
\usepackage{pgfpages}
\usepackage{float}
% citations
\usepackage{natbib}
\usepackage{lipsum}
\usepackage[export]{adjustbox}

\bibpunct{(}{)}{;}{a}{,}{,}
\def\citeapos#1{\citeauthor{#1}'s (\citeyear{#1})}
\renewcommand{\bibsection}{\subsubsection*{\bibname } }

@@

\begin{frame}
Federal Open Market Committee (FOMC): Maximum Employment, Stable Inflation, Financial Stability
\begin{figure}[H]
\includegraphics[width=1\textwidth]{../output/data_for_graphs/Topic-Model-3-topics.PNG}
\end{figure}
\vspace{-5mm}

Ngrams (unigrams to 10-grams)
\vspace{-1mm}
\begin{figure}[H]
\begin{center}
\includegraphics[width=.2\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
\includegraphics[width=.2\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
\end{center}
\end{figure}
\vspace{-5mm}

Reduced Features (stacked documents, larger Ngrams)
\vspace{-1mm}
\begin{figure}[H]
\includegraphics[width=.2\textwidth]{"../output/data_for_graphs/nn_40_40_f1_stacked".pdf}
\includegraphics[width=.2\textwidth]{"../output/data_for_graphs/nn_40_f1_stacked".pdf}
\includegraphics[width=.2\textwidth]{"../output/data_for_graphs/log_lasso_f1_stacked".pdf}
\includegraphics[width=.2\textwidth]{"../output/data_for_graphs/naive_bayes_f1_stacked".pdf}
\end{figure}
